### 2013-10-21 article.tex
Formatting of said tables.
Table formatting.

\usepackage{color}
\usepackage{float}
\usepackage{mdwlist}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{listings}

@@

@@

\begin{table}
\begin{center}
	\begin{tabular}{|l|l|l|}
		\hline
		\multicolumn{3}{|c|}{Int $200x200$} \\
		\hline
		~    & BASIC & TILE \\	\hline
		HARD	& 1.16    	& 0.24   	 \\	\hline
		SOFT	& 11610.02 	& 9866.40    	\\	\hline
		WARP & 15.31     	& 18.97   	\\	\hline
	\end{tabular}
	\label{tab:contribution:results:summaryint}
	\caption{Average exectution time (ms) of a integer matrix.}
\end{center}
\end{table}

\begin{table}
\begin{center}
	\begin{tabular}{|l|l|l|}
		\hline
		\multicolumn{3}{|c|}{Float $200x200$} \\
		\hline
		~    & BASIC & TILE \\	\hline
		HARD & 0.77     	& 0.22    		\\	\hline
		SOFT & 10247.03     & 10909.88    	\\	\hline
		WARP & 14.08     	& 17.44    		\\	\hline
	\end{tabular}
	\label{tab:contribution:results:summaryfloat}
	\caption{Average exectution time (ms) of a floating point matrix.}
\end{center}
\end{table}

@@

\subsubsection{WARP}
\label{sec:contribution:results:warp}
The \textit{GPU}-accelerated implementation show a clear improvement when utilizing memory.\footnote{Bad visualization.} According to Microsoft... However, the execution time of WARP-acceleration demonstrate an increase in execution time...
\begin{figure}[htb]
\begin{center}
	\resizebox{ \textwidth/2 }{!}{\input{msshard}}
	\caption{Hardware~Accelerated execution time with floating point-precision for Basic- and Tiled implementation, with visualized mean and standard deviations. Values outside of their respective standard deviations have been clipped for the sake of clarity.}
	\label{fig:contribution:results:warp:msshard}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
	\resizebox{ \textwidth/2 }{!}{\input{msswarp}}
	\caption{\textit{WARP} execution time with float-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations. Values outside of their respective standard deviations have been clipped for the sake of clarity.}
	\label{fig:contribution:results:warp:msswarp}
\end{center}
\end{figure}

>>>>

\usepackage{color}
\usepackage{float}
\usepackage{mdwlist}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{listings}

@@

\subsection{Process~of~Study}
\label{sec:contribution:processofstudy}
For the purpose of this study,

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILE}}	\\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& $1.16$			& $0.24$ 	& $-79.3\%$    				\\ \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $11610.02$		& $9866.40$	& $-15.0\%$     				\\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& $15.31$			& $18.97$	& $+23.9\%$     				\\ \hline
\end{tabular}
\label{tab:contribution:results:summaryint}
\caption{Average exectution time (ms) of a $200x200$ integer matrix.}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
							& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILE}}		\\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& $0.77$			& $0.22$		& $-71.4\%$    				\\ \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& $10247.03$		& $10909.88$	& $+6.5\%$     				\\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& $14.08$			& $17.44$		& $+23.9\%$    				\\ \hline
\end{tabular}
\label{tab:contribution:results:summaryfloat}
\caption{Average exectution time (ms) of a $200x200$ floating point matrix.}
\end{center}
\end{table}

@@

\subsubsection{WARP}
\label{sec:contribution:results:warp}
%In both int- and float-cases, warp performs worse with memory tiling, whereas ref-device is less impaired or even performs better. why?
The \textit{GPU}-accelerated implementation show a clear improvement when utilizing memory.\footnote{Bad visualization.} According to Microsoft... However, the execution time of WARP-acceleration demonstrate an increase in execution time...
\begin{figure}[htb]
\begin{center}
	\resizebox{ \columnwidth }{!}{\input{msshard}}
	\caption{Hardware~Accelerated execution time with floating point-precision for Basic- and Tiled implementation, with visualized mean and standard deviations. Values outside of their respective standard deviations have been clipped for the sake of clarity.}
	\label{fig:contribution:results:warp:msshard}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
	\resizebox{ \columnwidth }{!}{\input{msswarp}}
	\caption{\textit{WARP} execution time with float-precision for the Basic- and Tiled-kernel, with visualized mean and standard deviations. Values outside of their respective standard deviations have been clipped for the sake of clarity.}
	\label{fig:contribution:results:warp:msswarp}
\end{center}
\end{figure}
